Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-01-02 output/paper/_figures.qmd
Adapting tables and figures to style AJE.

- Figure titles and legends should be submitted as single paragraph.

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Marginal comparison results for $hitrtse \sim edc$
#| fig-width: 9
#| fig-height: 10

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Marginal comparison results for $production \sim edc$
#| fig-width: 9
#| fig-height: 12

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Marginal comparison results for $hitrtse \sim metabolite$
#| fig-width: 9
#| fig-height: 5

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```

>>>>

@@

::: {#fig-marginal-1}
```{r marginal-1}
#| fig-width: 9
#| fig-height: 10

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```
**Marginal contrasts (exposures: \acr{edcs}; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
Circles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

::: {#fig-marginal-2}
```{r marginal-2}
#| fig-width: 9
#| fig-height: 12

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```
**Marginal contrasts (exposures: \acr{edcs}; outcomes: glucocorticosteroids) (HELIX Study; 2013-2016).**
Circles, triangles, and squares indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

::: {#fig-marginal-3}
```{r marginal-3}
#| fig-width: 9
#| fig-height: 5

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```
**Marginal contrasts (exposures: glucocorticosteroids; outcome: \acr{hitrtse}) (HELIX Study; 2013-2016).**
Circles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

### 2024-01-02 output/paper/_si.qmd
Adapting tables and figures to style AJE.

::: {#supptbl-codebook-1}
```{r codebook-1}
codebook_1
```
Codebook for covariates used in $hitrtse \sim edc$
:::

::: {#supptbl-codebook-2}
```{r codebook-2}
codebook_2
```
Codebook for covariates used in $metabolite \sim edc$
:::

::: {#supptbl-codebook-3}
```{r codebook-3}
codebook_3
```
Codebook for covariates used in $hitrtse \sim metabolite$
:::

@@

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name)
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
Information about non-persistent EDCs
:::

@@

::: {#supptbl-info-mets}
```{r info-mets}
mets_info <- readODS::read_ods(
  path = here::here("docs", "steroids.ods")
) |>
  tidylog::select(analyte, acronym, type, hmdb_id, cas_number)
gt::gt(mets_info,
       groupname_col = "type") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    analyte = "Metabolite",
    acronym = "Symbol",
    hmdb_id = "HMDB ID",
    cas_number = "CAS number"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_footnote(
    footnote = "Human Metabolome Database",
    locations = gt::cells_column_labels(
      columns = hmdb_id
    )
  ) |>
  gt::tab_footnote(
    footnote = "Chemical Abstracts Service",
    locations = gt::cells_column_labels(
      columns = cas_number
    )
  )
```
Information about metabolites
:::

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    lloq = "loq"
  )
gt::gt(lloq_mets |> dplyr::arrange(metabolite)) |>
  gt::tab_footnote(
    footnote = "Lower limit of quantification expressed in nanograms per millilitre.",
    locations = gt::cells_column_labels(
      columns = lloq
    )
  )
```
Lower limits of quantification for the glucocorticosteroids
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```
Effective sample size before and after weights estimation for $hitrtse \sim edc$
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```
Effective sample size before and after weights estimation for $metabolite \sim edc$
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "N.",
    locations = gt::cells_column_labels(
      columns = c(Unadjusted, Adjusted)
    )
  ) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  )
```
Effective sample size before and after weights estimation for $hitrtse \sim metabolite$
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights for $hitrtse \sim edc$
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights for $metabolite \sim edc$
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights for $hitrtse \sim metabolite$
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for $hitrtse \sim edc \times sex$
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for $metabolite \sim edc \times sex$
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for $hitrtse \sim metabolite \times sex$
:::

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
Classification of the measured non-persistent EDCs, by cohort.
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
Classification of the measured glucocorticosteroids, by cohort.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal contrast results for $hitrtse \sim edc \times sex$
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal contrast results for $metabolite \sim edc \times sex$
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal contrast results for $hitrtse \sim metabolite \times sex$
:::

>>>>

::: {#supptbl-codebook-1}
```{r codebook-1}
codebook_1
```
Codebook for the covariates used in the estimation of the marginal comparisons of \acr{edcs} on \acr{hitrtse}.
:::

::: {#supptbl-codebook-2}
```{r codebook-2}
codebook_2
```
Codebook for the covariates used in the estimation of the marginal comparisons of \acr{edcs} on the glucocorticosteroids.
:::

::: {#supptbl-codebook-3}
```{r codebook-3}
codebook_3
```
Codebook for the covariates used in the estimation of the marginal comparisons of the glucocorticosteroids on \acr{hitrtse}.
:::

@@

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name)
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
Information about non-persistent EDCs, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.
:::

@@

::: {#supptbl-info-mets}
```{r info-mets}
mets_info <- readODS::read_ods(
  path = here::here("docs", "steroids.ods")
) |>
  tidylog::select(analyte, acronym, type, hmdb_id, cas_number)
gt::gt(mets_info,
       groupname_col = "type") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    analyte = "Metabolite",
    acronym = "Symbol",
    hmdb_id = "HMDB ID",
    cas_number = "CAS number"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_footnote(
    footnote = "Abbreviations: Human Metabolome Database (HMDB); Chemical Abstracts Service (CAS).",
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Information about the glucocorticosteroids, including the full metabolite name, the standard symbol, the identifier from the HMDB, and the CAS number.
:::

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite)
gt::gt(lloq_mets |> dplyr::arrange(Metabolite)) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ), expressed in nanograms per millilitre."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Lower limits of quantification for the glucocorticosteroids.
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcome: \acr{hitrtse}).
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Effective sample size before and after balancing weights estimation (exposures: \acr{edcs}; outcomes: glucocorticosteroids).
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: \acr{hitrtse}).
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcome: \acr{hitrtse}).
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights (exposures: \acr{edcs}; outcomes: glucocorticosteroids).
:::

::: {#supptbl-weights-3}
```{r weights-3}
tidy_res_weighted_fits(
  dat_tbl = weights_3$dat_tbl,
  dat_plt = weights_3$dat_plt,
  sa_var = NULL
)$table
```
Summary statistics of the estimated balancing weights (exposures: glucocorticosteroids; outcome: \acr{hitrtse}).
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcome: \acr{hitrtse}; modifier: sex).
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for effect modification (exposures: \acr{edcs}; outcomes: glucocorticosteroids; modifier: sex).
:::

::: {#supptbl-weights-3sa}
```{r weights-3sa}
tidy_res_weighted_fits(
  dat_tbl = weights_3SA$dat_tbl,
  dat_plt = weights_3SA$dat_plt,
  sa_var = "e3_sex"
)$table
```
Summary statistics of the estimated balancing weights for effect modification (exposures: glucocorticosteroids; outcome: \acr{hitrtse}; modifier: sex).
:::

@@

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)$plot
```
**Measurement classification of \acr{edcs}, by cohort.**
Coding: 1, quantifiable; 2, <LOD; 3, interference or out of range; 4. not analysed.
:::

@@

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var,
                              st = 1, en = 3) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest(append_to_chem = NULL)$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)$plot
```
**Measurement classification of the glucocorticosteroids, by cohort.**
Coding: 1, quantifiable; 2, <LOQ; 3, interference or out of range; 4, not detected.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: \acr{edcs}; outcome: \acr{hitrtse}; modifier: sex) (HELIX Study; 2013-2016).**
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: \acr{edcs}; outcomes: glucocorticosteroids; modifier: sex) (HELIX Study; 2013-2016).**
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

@@

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
**Marginal contrasts for effect modification (exposures: glucocorticosteroids; outcome: \acr{hitrtse}; modifier: sex) (HELIX Study; 2013-2016).**
Circles and triangles indicate effect estimates. Solid lines indicate the $95\%$ \acr{ci}.
:::

### 2024-01-02 output/paper/_tables.qmd
Adapting tables and figures to style AJE.

**Table titles should give details on the place of the study, the time of the study, and the study population (if applicable). Example, “Baseline Characteristics of Infants With Initial and Follow-up Screening, London, United Kingdom, 2001–2003.” In the table body, leave blank spaces for no entry; avoid using dashes. Order of footnotes: 1) Abbreviations: (no footnote symbol, listed alphabetically, separated by semicolons); 2) other footnotes as necessary, each preceded by a superscript lowercase letter. Footnotes must be cited in order when reading from left to right and top to bottom.**

@@

```{r hypothesis-1}
#| label: tbl-hypothesis-1
#| tbl-cap: Hypothesis testing results of effect modification by sex for $hitrtse \sim edc$.

@@

```{r hypothesis-2}
#| label: tbl-hypothesis-2
#| tbl-cap: Hypothesis testing results of effect modification by sex for $metabolite \sim edc$.

@@

```{r hypothesis-3}
#| label: tbl-hypothesis-3
#| tbl-cap: Hypothesis testing results of effect modification by sex for $hitrtse \sim metabolite$.

>>>>

@@

```{r hypothesis-1}
#| label: tbl-hypothesis-1
#| tbl-cap: Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on \acr{hitrtse} (HELIX Study; 2013-2016).

@@

```{r hypothesis-2}
#| label: tbl-hypothesis-2
#| tbl-cap: Pairwise differences between sex-specific marginal contrasts for the effect of \acr{edcs} on the glucocorticosteroids (HELIX Study; 2013-2016).

@@

```{r hypothesis-3}
#| label: tbl-hypothesis-3
#| tbl-cap: Pairwise differences between sex-specific marginal contrasts for the effect of the glucocorticosteroids on \acr{hitrtse} (HELIX Study; 2013-2016).
